The hydra and the rooster

### 2020-08-20 latex/chapter-ordinals.tex
typo corrections in *.tex

\begin{remark}
 The proof of \texttt{compare\_correct} uses a well-know pattern of \coq{}.
Let us consider  the following subgoal.

@@

We have now to prove that two proofs of \texttt{Nat.ltb x0 (S n)} are equal.

This is not obvious, but  a consequence of the following lemma of library 
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Logic.Eqdep_dec.html}{Coq.Logic.Eqdep\_dec}.

@@

Thus unicity of proofs of \texttt{Nat.ltb x0 (S n)}  comes from the decidability of
equality on type \texttt{bool}.

This is why we used the boolean function \texttt{Nat.ltb} instead of the inductive predicate \texttt{Nat.lt} in the definition of type \texttt{t $n$} (see page~\pageref{def: Finite-ord-type}).

For more information about this pattern, please look at the numerous mailing lists and 
FAQs on \coq{}).

@@

Applying lemmas of the libraries \texttt{Coq.Wellfounded.Inverse\_Image}, \linebreak
 \texttt{Coq.Wellfounded.Inclusion}, and \texttt{Coq.Arith.Wf\_nat}, we prove that our
relation \texttt{wf} is well founded.

@@

Finally, it is interesting to show that, if $i<j$, then the segment $[0,i)$ is a ``sub-segment'' of
$[0,j)$. Since the terms  $t\;i$ and $t\;j$ are not convertible, we consider a ``cast'' 
function $\iota$ from $t\;i$ to $t\;j$, and prove this function is  a bijection  from $t\;i$ to
the segment $[0,i)$ of $t\;j$.

>>>>

\begin{remark}
 The proof of \texttt{compare\_correct} uses a well-known pattern of \coq{}.
Let us consider  the following subgoal.

@@

We have now to prove that there exists at most one  proof of \texttt{Nat.ltb x0 (S n)}. This is not obvious, but  a consequence of the following lemma of library 
\href{https://coq.inria.fr/distrib/current/stdlib/Coq.Logic.Eqdep_dec.html}{Coq.Logic.Eqdep\_dec}.

@@

Thus unicity of proofs of \texttt{Nat.ltb x0 (S n)}  comes from the decidability of
equality on type \texttt{bool}.
This is why we used the boolean function \texttt{Nat.ltb} instead of the inductive predicate \texttt{Nat.lt} in the definition of type \texttt{t $n$} (see page~\pageref{def: Finite-ord-type}).
For more information about this pattern, please look at the numerous mailing lists and 
FAQs on \coq{}).

@@

Applying lemmas of the libraries \texttt{Coq.Wellfounded.Inverse\_Image}, \linebreak
 \texttt{Coq.Wellfounded.Inclusion}, and \texttt{Coq.Arith.Wf\_nat}, we prove that our
relation \texttt{lt} is well founded.

@@

Finally, it is interesting to show that, if $i<j$, then the segment $[0,i)$ is a ``sub-segment'' of
$[0,j)$. Since the terms  ($t\;i$) and ($t\;j$) are not convertible, we consider a ``cast'' 
function $\iota$ from ($t\;i$) into ($t\;j$), and prove that this function is  a monotonous bijection  from ($t\;i$) to
the segment $[0,i)$ of ($t\;j$).
